Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-07-25 apj.tex
writing more stuff

\color{purple}
For brevity, we do not present here the analysis of simulated data used to validate and quantify bias in our results.
The simulation tests in \S\ref{model2:sec} are representative for both Model~1 of this Section and Model~2 of the subsequent section.
\color{black}

@@

We compare our model and its color-coefficient parameters $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models \citep[e.g][]{1989ApJ...345..245C}.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish parameters of the \citetalias{1999PASP..111...63F} model.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%;
\color{red}
for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error amplitude in Eqn.~\ref{f99:eqn} is $<0.008$ mag.
\color{black}

Our model can be expressed as
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V).
\end{equation}
Our median-fit values for the $\pmb{\gamma}$ coefficients,
%---- fitz11.py
$\frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  =\{4.80 ,   3.89,   2.89,   2.22,   1.59\}$ and
$ \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}=\{-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71\}$,
%----
can be transformed to a basis composed of the $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $a$ and $b$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.82 & 1.15  \\
-5.27 & 0.72
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_{\gamma^0} \\
\vec{\epsilon}_{\gamma^1}
\end{pmatrix},
\label{trans_I:eqn}
\end{equation}
where the two residual vectors
\begin{align}
\begin{split}
\vec{\epsilon}_{\gamma^0} &=\{0.06, -0.07, -0.07,  0.07, 0.02\}, \\
\vec{\epsilon}_{\gamma^1} & =\{-0.06, 0.16, -0.22, 0.33, -0.26\}
\end{split}
\label{res_I:eqn}
\end{align}
quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.

This result indicates that
the allowed variation in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are closely aligned.
That is to say, with no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.

The above result is visualized in Figure~\ref{plane:fig}, which  shows two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma_X/(\gamma_B-\gamma_V)$ of our model (solid lines),
and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$, and close to coplanar in $BVR$.  The $a$ and $b$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
vectors are bases for almost the same plane in the 5-dimensional color space, and can be transformed between themselves through rotation.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11/plane0.pdf}
   \includegraphics[width=2.95in]{output11/plane1.pdf}
%   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
%   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
   \caption{
   \color{purple}
   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
   magnitudes in 5-bands $UBVRI$ this visualization shows only $UVI$.   The left and right plots show the same information from
   two different perspectives.
   Our model is shown in solid-line unit vectors in the directions of $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$. The only possible magnitudes possible
   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
   in the directions of  $a(X)$, $b(X)$; the only possible magnitudes possible are confined to the plane that contains both.
   The perspective on the right visually show that all four vectors are nearly coplanar.  
   The combination $a(X)+b(X)/2.44$ is shown in the dotted red
   line: it is almost perfectly superimposed on $\pmb{\gamma}^0$.
   \label{plane:fig}}
\end{figure}

When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $a$ and $b$.
However the linear model does not specify zero dust so the origin of gamma is unspecified.
The general result is that the magnitude planes of the linear and dust models are parallel.
Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models, and determines the choice of directions of
the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.  Suppose that the data were described by a dust model.  Then a \citetalias{1999PASP..111...63F}  dust model 
can be written as 
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ providing freedom in the directions of the two basis vectors.
The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
%perturbations from a fixed $R^F_0$ is
%\begin{equation}
%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
%\end{equation}
%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.

@@

\color{red}
The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
in terms of the $a$ and $b$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
\color{black}
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V} \\
\frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V} \\
\frac{\delta_X}{\delta_U} \\
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.88 & 1.16 \\
-5.00 & 0.73 \\
0.24 & 0.46
\end{array}
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\begin{pmatrix}
\vec{\epsilon}_{\gamma^0} \\
\vec{\epsilon}_{\gamma^1} \\
\vec{\epsilon}_{\delta}
\end{pmatrix},
\label{model2trans:eqn}
\end{equation}
where the residual vectors
\begin{align}
\begin{split}
\vec{\epsilon}_{\gamma^0} &=\{0.07, -0.07, -0.07,  0.06,  0.02\},\\
\vec{\epsilon}_{\gamma^1} &=\{ -0.04, 0.14,  -0.24,  0.32, -0.22\},\\
\vec{\epsilon}_{\delta} &=\{ -0.05, 0.08,  -0.03,  -0.09, -0.12\}
\end{split}
\label{model2res:eqn}
\end{align}
are perpendicular to $a$ and $b$.
The $\pmb{\gamma}$ residuals $\vec{\epsilon}_{\gamma^0}$ and
$\vec{\epsilon}_{\gamma^1} $
quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
\color{red}
 $\pmb{\delta}$ too
has a significant projection onto the dust plane, as the $\vec{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
The transformation yields
a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.
\color{black}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{+0.0009}_{-0.0010}$
&
$0.0016^{+0.0008}_{-0.0008}$
&
$0.0016^{+0.0007}_{-0.0007}$
&
$0.0015^{+0.0006}_{-0.0005}$
&
$0.0028^{+0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.7^{+   0.9}_{  -0.4}$
&
$  -0.0^{+   0.1}_{  -0.2}$
&
$ \ldots$
&
$  -0.1^{+   0.1}_{  -0.1}$
&
$   0.7^{+   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.035^{+ 0.005}_{-0.005}$
&
$ 0.026^{+ 0.004}_{-0.004}$
&
$ 0.023^{+ 0.004}_{-0.004}$
&
$ 0.020^{+ 0.003}_{-0.003}$
&
$ 0.017^{+ 0.003}_{-0.003}$
\\
${\beta_X/\beta_V-1}$
&
$  0.54^{+  0.12}_{ -0.10}$
&
$  0.16^{+  0.06}_{ -0.06}$
&
$ \ldots$
&
$ -0.12^{+  0.03}_{ -0.03}$
&
$ -0.26^{+  0.06}_{ -0.06}$
\\
$\eta_X$
&
$0.0007^{+0.0012}_{-0.0012}$
&
$0.0006^{+0.0010}_{-0.0010}$
&
$0.0011^{+0.0008}_{-0.0008}$
&
$0.0010^{+0.0007}_{-0.0007}$
&
$0.0003^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.24^{+  0.47}_{ -0.98}$
&
$ -0.32^{+  0.30}_{ -0.76}$
&
$ \ldots$
&
$ -0.08^{+  0.20}_{ -0.13}$
&
$ -0.66^{+  0.29}_{ -0.58}$
\\
$\zeta_X$
&
$  0.01^{+  0.04}_{ -0.04}$
&
$ -0.01^{+  0.03}_{ -0.03}$
&
$ -0.03^{+  0.03}_{ -0.03}$
&
$ -0.01^{+  0.02}_{ -0.02}$
&
$ -0.03^{+  0.02}_{ -0.02}$
\\
${\zeta_X/\zeta_V-1}$
&
$ -0.91^{+  0.75}_{ -1.78}$
&
$ -0.62^{+  0.46}_{ -1.15}$
&
$ \ldots$
&
$ -0.50^{+  0.21}_{ -0.53}$
&
$ -0.18^{+  0.41}_{ -0.32}$
\\
$\gamma^0_X$
&
$ 62.57^{+  3.71}_{ -3.66}$
&
$ 51.36^{+  3.12}_{ -3.13}$
&
$ 38.26^{+  2.67}_{ -2.69}$
&
$ 29.03^{+  2.36}_{ -2.39}$
&
$ 20.40^{+  2.21}_{ -2.26}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.63^{+  0.06}_{ -0.05}$
&
$  0.34^{+  0.03}_{ -0.03}$
&
$ \ldots$
&
$ -0.24^{+  0.01}_{ -0.02}$
&
$ -0.47^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.27^{+  3.50}_{ -3.75}$
&
$-11.08^{+  2.92}_{ -3.18}$
&
$-14.99^{+  2.38}_{ -2.66}$
&
$-14.28^{+  2.05}_{ -2.22}$
&
$-13.27^{+  1.91}_{ -2.09}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.38^{+  0.15}_{ -0.18}$
&
$ -0.26^{+  0.09}_{ -0.11}$
&
$ \ldots$
&
$ -0.05^{+  0.04}_{ -0.04}$
&
$ -0.12^{+  0.09}_{ -0.08}$
\\
$\delta_X$
&
$  1.98^{+  0.52}_{ -0.50}$
&
$ -2.13^{+  0.55}_{ -0.54}$
&
$ -1.84^{+  0.51}_{ -0.52}$
&
$  0.70^{+  0.33}_{ -0.35}$
&
$  1.72^{+  0.75}_{ -0.73}$
\\
${{\delta_X/\delta_I-1}}$
&
$  0.17^{+  0.50}_{ -0.27}$
&
$ -2.23^{+  0.30}_{ -0.64}$
&
$ -2.08^{+  0.25}_{ -0.44}$
&
$ -0.60^{+  0.54}_{ -0.24}$
&
$ \ldots$
\\
$\sigma_X$
&
$ 0.048^{+ 0.012}_{-0.011}$
&
$ 0.027^{+ 0.007}_{-0.007}$
&
$ 0.014^{+ 0.004}_{-0.005}$
&
$ 0.008^{+ 0.006}_{-0.005}$
&
$ 0.041^{+ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
\end{table}

>>>>

@@

We compare our model and its color-coefficient parameters $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$ with the expectations of  dust models.
The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models \citep[e.g.][]{1989ApJ...345..245C}.
For the case of
$R^F=2.5$ and $A^F_V=0.1$ dust attenuating light from the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$\mathbf{a} = (0.96,   1.00,   1.00,   0.97,   0.77)$ and $\mathbf{b}=(  1.77,   0.98,   0.12,  -0.50,  -0.53)$.
The $F$ superscript distinguishes parameters of the \citetalias{1999PASP..111...63F} model.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%;
\color{red}
for $0\le A^F_V\le 1$ and $2 \le R^F \le 3.5$, the largest error in Eqn.~\ref{f99:eqn} has amplitude $<0.008$ mag.
\color{black}

The extrinsic contribution to our model can be re-expressed to have a similar parameterization
\begin{equation}
A_X = \frac{\gamma^0_X}{\gamma^0_B-\gamma^0_V}  E_{\gamma^0}(B-V) +  \frac{\gamma^1_X}{\gamma^1_B-\gamma^1_V}  E_{\gamma^1}(B-V),
\end{equation}
where $E_{\gamma^i}(B-V) \equiv  (\gamma^i_B-\gamma^i_V)k_i$.
Our median-fit values for the $\pmb{\gamma}$ coefficients are
%---- fitz11.py
$\frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V}  =(4.80 ,   3.89,   2.89,   2.22,   1.59)$ and
$ \frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V}=(-3.83 ,  -4.42,  -5.42,  -5.15,  -4.71)$.
%----

Our model $\gamma$-based vectors can be written in terms of the 
dust-based $a(X)$ and $b(X)$ vectors plus a residual vector perpendicular to $\mathbf{a}$ and $\mathbf{b}$.
The result is
\begin{equation}
\begin{pmatrix}
 \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} 
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.82 & 1.15  \\
-5.27 & 0.72
\end{array}
\end{pmatrix} 
\begin{pmatrix}
\mathbf{a} \\
\mathbf{b}
\end{pmatrix}+
\begin{pmatrix}
\pmb{\epsilon}_{\gamma^0} \\
\pmb{\epsilon}_{\gamma^1}
\end{pmatrix},
\label{trans_I:eqn}
\end{equation}
where the two residual vectors
\begin{align}
\begin{split}
\pmb{\epsilon}_{\gamma^0} &=(0.06, -0.07, -0.07,  0.07, 0.02), \\
\pmb{\epsilon}_{\gamma^1} & =(-0.06, 0.16, -0.22, 0.33, -0.26)
\end{split}
\label{res_I:eqn}
\end{align}
quadratically contribute  0.03\% and 0.2\% respectively to the total  length of the $\pmb{\gamma}$ vectors.
This result indicates that
the allowed variations in $UBVRI$ allowed by the \citetalias{1999PASP..111...63F} model and our best-fit model are confined to near-parallel 2-dimensional
planes within
the 5-dimensional magnitude space.
Wiith no prior assumptions of dust extinction behavior or the distribution of $A_V$, the supernova data themselves exhibit
2-dimensional color variations that are closely aligned with the 2-dimensional color variations predicted by the \citetalias{1999PASP..111...63F} dust model.

The above result is visualized in Figure~\ref{plane:fig}, which  shows  in the $UVI$-subspace two perspectives (left and right columns)
of the unit vectors corresponding to $\pmb{\gamma}^0$ and  $\pmb{\gamma}^1$ of our model (solid lines),
and $\mathbf{a}$, $\mathbf{b}$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  All $\pmb{\gamma}$ vectors are chosen to intersect the origin.
The two perspectives show that while the four vectors point in different directions for each band combination,
they are almost coplanar in $UVI$ (they are slightly less coplanar in $BVR$).  The $\mathbf{a}$ and $\mathbf{b}$ vectors and the $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$
vectors span near-parallel planes in the 5-dimensional color space, and hence each pair can be almost entirely expressed in  terms of
the other pair.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11/plane0.pdf}
   \includegraphics[width=2.95in]{output11/plane1.pdf}
%   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
%   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
   \caption{
   \color{purple}
   Visualization of how supernova magnitudes can vary in our model and that of \citetalias{1999PASP..111...63F}.  While the models describe
   magnitudes in 5-bands $UBVRI$ this visualization shows only $UVI$.   The left and right plots show the same information from
   two different perspectives.
   Our model is shown in solid-line unit vectors in the directions of $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$. The only possible magnitudes possible
   are a linear combination of these two vectors, and hence are confined to the plane that contains both.
   The  \citetalias{1999PASP..111...63F} model is shown in dashed-line unit vectors
   in the directions of  $\mathbf{a}$, $\mathbf{b}$; the only possible magnitudes possible are confined to the plane that contains both.
   The perspective on the right visually show that all four vectors are nearly coplanar.  
   The combination $\mathbf{a}+\mathbf{b}/2.44$ is shown in the dotted red
   line: it is almost perfectly superimposed on $\pmb{\gamma}^0$.
   \label{plane:fig}}
\end{figure}

%When fixing the origin of $\pmb{\gamma}$ to zero, the $\pmb{\gamma}$ vectors are found to be coplanar with $\mathbf{a}$ and $\mathbf{b}$.
%While the  $\gamma$ vectors define a plane,  is unspecified.
%The linear model does not specify zero dust so the origin of the $\gamma$'s is unspecified.
%The general result is that the magnitude planes of the linear and dust models are parallel.
%Color changes are consistent between the two models but there is no specification of the relation between $k^0$ and $k^1$ with $A_V$ and $E(B-V)$.

%The dust model expressed in Eqn.~\ref{f99:eqn} can be reparameterized as
%\begin{equation}
%A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
%\label{f99:eqn}
%\end{equation}
%where $R=A_V/E(B-V)$.

Suppose that the data were due to a dust model with constant $R \equiv A_V/E(B-V)$.
The  $A_V$ and $E(B-V)$ parameters of the dust model in Eqn.~\ref{f99:eqn} would then be correlated.
An alternative parameterization 
\begin{equation}
A_X = A_V \left(a(X)  +  \frac{b(X)}{R}\right),
\end{equation}

A prior that $k_0$ and  $k_1$ be uncorrelated was enforced to break degeneracies in our linear models.
These determine the choice of directions of
the vectors $\pmb{\gamma}^0$ and $\pmb{\gamma}^1$.
and so the $\gamma$'s

   Then a \citetalias{1999PASP..111...63F}  dust model 
can be written in a new basis
%To see how this prior would operate on dust models, consider that themodel in Eqn.~\ref{f99:eqn} can
%be expressed in terms of new basis vectors parametrized by $\kappa$:
\begin{equation}
A_X =  (1-\kappa_1 \kappa_2)^{-1} [(A^F_V - \kappa_2 E^F(B-V))\left(a(X)+\kappa_1 b(X) \right) +  (-\kappa_1 A^F_V + E^F(B-V)) (\kappa_2 a(X) + b(X))],
\end{equation}
with the parameters $\kappa_1$ and $\kappa_2$ parameterizing the directions of the two new basis vectors.
The vector $a(X)+\kappa_1 b(X)$ represents extinction that can occur with fixed $R^F_0=1/\kappa_1$ and unconstrained $\kappa_2$.
%While a similar interpretation could be made of $\kappa_2 a(X) + b(X)$, note that to first order the extinction for $\Delta R$
%perturbations from a fixed $R^F_0$ is
%\begin{equation}
%A_X = A_V \left(a(X) + \left(\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0} \right) b(X) \right).
%\end{equation}
%Then $\kappa^{-1}_2$ can this be associated with $\frac{1}{R^F_0} - \frac{\Delta R^F}{R^F_0}$.

@@

\color{red}
The newly fitted $\pmb{\gamma}$ and  $\pmb{\delta}$ vectors (the latter normalized by $\delta_U$) can be expressed 
in terms of the $\mathbf{a}$ and $\mathbf{b}$ vectors that describe the \citetalias{1999PASP..111...63F} dust model
\color{black}
\begin{equation}
\begin{pmatrix}
 \frac{\pmb{\gamma}^0}{\gamma^0_B-\gamma^0_V} \\
\frac{\pmb{\gamma}^1}{\gamma^1_B-\gamma^1_V} \\
\frac{\delta_X}{\delta_U} \\
\end{pmatrix}=
\begin{pmatrix}
\begin{array}{rr}
2.88 & 1.16 \\
-5.00 & 0.73 \\
0.24 & 0.46
\end{array}
\end{pmatrix} 
\begin{pmatrix}
\mathbf{a} \\
\mathbf{b}
\end{pmatrix}+
\begin{pmatrix}
\pmb{\epsilon}_{\gamma^0} \\
\pmb{\epsilon}_{\gamma^1} \\
\pmb{\epsilon}_{\delta}
\end{pmatrix},
\label{model2trans:eqn}
\end{equation}
where the residual vectors
\begin{align}
\begin{split}
\pmb{\epsilon}_{\gamma^0} &=(0.07, -0.07, -0.07,  0.06,  0.02),\\
\pmb{\epsilon}_{\gamma^1} &=( -0.04, 0.14,  -0.24,  0.32, -0.22),\\
\pmb{\epsilon}_{\delta} &=(-0.05, 0.08,  -0.03,  -0.09, -0.12)
\end{split}
\label{model2res:eqn}
\end{align}
are perpendicular to $a$ and $b$.
The $\pmb{\gamma}$ residuals $\pmb{\epsilon}_{\gamma^0}$ and
$\pmb{\epsilon}_{\gamma^1} $
quadratically contribute 0.03\% and 0.2\% to the total  lengths of the vectors, meaning that most
of the $\pmb{\gamma}$'s project onto the plane predicted by the \citetalias{1999PASP..111...63F} dust model.
\color{red}
 $\pmb{\delta}$ too
has a significant projection onto the dust plane, as the $\pmb{\epsilon}_{\delta}$ residual contributes 2\% of the length of the $\pmb{\delta}$ vector.
The transformation yields
a 68\%-ile  credible interval for $R^F$ of  $2.31$--$2.69$, slightly shifted higher relative to the results of Model~I.
\color{black}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Parameters & $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0037^{+0.0010}_{-0.0010}$
&
$0.0011^{+0.0008}_{-0.0008}$
&
$0.0013^{+0.0007}_{-0.0007}$
&
$0.0013^{+0.0006}_{-0.0006}$
&
$0.0026^{+0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.7^{+   1.3}_{  -0.5}$
&
$  -0.1^{+   0.2}_{  -0.4}$
&
$   0.0^{+   0.0}_{   0.0}$
&
$  -0.0^{+   0.2}_{  -0.1}$
&
$   1.0^{+   1.2}_{  -0.5}$
\\
$\beta_X$
&
$ 0.034^{+ 0.006}_{-0.005}$
&
$ 0.026^{+ 0.005}_{-0.005}$
&
$ 0.023^{+ 0.004}_{-0.004}$
&
$ 0.020^{+ 0.003}_{-0.003}$
&
$ 0.017^{+ 0.003}_{-0.003}$
\\
${\beta_X/\beta_V-1}$
&
$  0.50^{+  0.11}_{ -0.10}$
&
$  0.15^{+  0.06}_{ -0.06}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.12^{+  0.03}_{ -0.03}$
&
$ -0.26^{+  0.06}_{ -0.06}$
\\
$\eta_X$
&
$0.0002^{+0.0011}_{-0.0011}$
&
$0.0004^{+0.0009}_{-0.0009}$
&
$0.0009^{+0.0008}_{-0.0008}$
&
$0.0008^{+0.0007}_{-0.0007}$
&
$0.0000^{+0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.47^{+  0.69}_{ -1.37}$
&
$ -0.39^{+  0.41}_{ -0.93}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.12^{+  0.19}_{ -0.16}$
&
$ -0.78^{+  0.42}_{ -0.88}$
\\
$\zeta_X$
&
$  0.01^{+  0.04}_{ -0.04}$
&
$ -0.00^{+  0.03}_{ -0.03}$
&
$ -0.03^{+  0.03}_{ -0.03}$
&
$ -0.01^{+  0.02}_{ -0.02}$
&
$ -0.03^{+  0.02}_{ -0.02}$
\\
${\zeta_X/\zeta_V-1}$
&
$ -0.78^{+  1.55}_{ -1.96}$
&
$ -0.62^{+  1.21}_{ -1.33}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.46^{+  0.45}_{ -0.52}$
&
$ -0.14^{+  0.51}_{ -0.42}$
\\
$\gamma^0_X$
&
$ 59.51^{+  4.09}_{ -4.09}$
&
$ 49.02^{+  3.32}_{ -3.30}$
&
$ 36.96^{+  2.69}_{ -2.70}$
&
$ 28.37^{+  2.36}_{ -2.36}$
&
$ 20.35^{+  2.16}_{ -2.16}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.61^{+  0.06}_{ -0.05}$
&
$  0.33^{+  0.03}_{ -0.03}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.23^{+  0.01}_{ -0.01}$
&
$ -0.45^{+  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -7.57^{+  3.75}_{ -4.06}$
&
$ -9.63^{+  2.90}_{ -3.27}$
&
$-13.65^{+  2.36}_{ -2.60}$
&
$-12.98^{+  2.08}_{ -2.27}$
&
$-12.16^{+  2.08}_{ -2.19}$
\\
${\gamma^1_X/\gamma^1_V-1}$
&
$ -0.44^{+  0.19}_{ -0.24}$
&
$ -0.30^{+  0.11}_{ -0.13}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.05^{+  0.05}_{ -0.05}$
&
$ -0.11^{+  0.11}_{ -0.10}$
\\
$\delta_X$
&
$  0.14^{+  1.13}_{ -1.41}$
&
$  0.11^{+  0.91}_{ -1.10}$
&
$  0.04^{+  0.56}_{ -0.60}$
&
$  0.01^{+  0.43}_{ -0.43}$
&
$ -0.02^{+  0.43}_{ -0.41}$
\\
${{\delta_X/\delta_U-1}}$
&
$  0.00^{+  0.00}_{  0.00}$
&
$ -0.22^{+  0.28}_{ -0.21}$
&
$ -0.63^{+  0.33}_{ -0.36}$
&
$ -0.82^{+  0.30}_{ -0.44}$
&
$ -1.05^{+  0.35}_{ -0.63}$
\\
$\sigma_X$
&
$ 0.053^{+ 0.008}_{-0.011}$
&
$ 0.018^{+ 0.011}_{-0.011}$
&
$ 0.017^{+ 0.004}_{-0.006}$
&
$ 0.010^{+ 0.007}_{-0.007}$
&
$ 0.040^{+ 0.006}_{-0.005}$
\\
\hline
\end{tabular}
\caption{68\% credible intervals for the Global Fit Parameters including the light-curve shape parameter, $x_1$ \label{globalx1:tab}}
\end{table}
